Switch equivalence and weak prime domains for left-linear DPO rewriting systems

### 2025-03-07 full_version/leftlinear.tex

\begin{lemma}
	equivalenze

	\begin{enumerate}
		\item 
		\item 
	\end{enumerate}
\end{lemma}
\begin{proof}
	contenuto...
\end{proof}

>>>>

\begin{lemma}

Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^1$ be a derivation of length $2$ and $(i_0, i_1)$ an independence pair between $\dder{D}_0$ and $\dder{D}_1$. Given a pre-switch $\der{E}$ for $\der{D}$ along $(i_0, i_1)$, the following are equivalent:
	\begin{enumerate}
		\item $\der{E}$ is a switch;
		\item if $(P, \{p_i\}_{i=0}^1)$ is a pullback for $f_{\der{D},1}$ along $g_{\der{D},0}$, then $\iota_{\der{E}}$
	\end{enumerate}
\end{lemma}
\begin{proof}
	contenuto...
\end{proof}
